\propertitle

### 2019-11-15 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-15T21:36:39+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

This fact is important for our analysis. If, say, means and pairwise
correlations seem informationally sufficient for a particular sample from a
brain area, then they may well be \emph{insufficient} for the full network
of neurons constituting that area, and vice versa. If what interests us is
\enquote{cooperativity} or \enquote{interaction} of a brain area, we cannot
therefore reliably use maximum-entropy distributions \emph{for a sample
  only} thereof. Yet the neuroscientific literature is besprinkled with
such sample-level analyses
\citep[\eg][]{martignonetal1995,bohteetal2000,schneidmanetal2006,shlensetal2006,barreiroetal2010,ganmoretal2011,granotatedgietal2013}.
The approach presented here bypasses this problem instead, because the
maximum-entropy method is applied to obtain the distribution of the full
network, not of the sample alone.

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/trunct_comparison_marginals.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
% comparison_ME_sample_full_levels.nb
%
% relentropies of sample2mom, marg2mom, sample4mom, marg4mom:
% -322.72, -85.7627, -42.8005, -4.23746 nats =
% -1401.56, -372.462, -185.88, -18.403 db
% correspond to probability ratios of
% 1., 8.11718\times 10^{102}, 3.69524\times 10^{121}, 2.06704\times 10^{138}
%
% difference in relentropies between 4 mom and 2 mom:
% sample level: 279.92 nats = 1215.68 db
% marg level: 81.5252 nats =  354.059 db
% correspond to prob ratios of
% 3.69524\times 10^{121},2.5465\times 10^{35}
%
% comparison_ME_sample_full_levels.nb
%

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-16T00:42:52+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

This fact is important for our analysis. If, say, means and pairwise
correlations seem informationally sufficient for a particular sample from a
brain area, then they may well not be sufficient for the full network of
neurons constituting that area, and vice versa. So if what interests us is
\enquote{cooperativity} or \enquote{interaction} of a brain area, it is
unreliable to use a maximum-entropy distribution constructed only for the
sample. % \citep[contrast this with some literature, \eg][]{martignonetal1995,bohteetal2000,schneidmanetal2006,shlensetal2006,barreiroetal2010,ganmoretal2011,granotatedgietal2013}
The approach presented here avoids this problem, because the
maximum-entropy method is applied to obtain the distribution of the full
network, not of the sample alone.

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/trunct_comparison_marginals.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
% comparison_ME_sample_full_levels.nb
%
% relentropies of sample2mom, marg2mom, sample4mom, marg4mom, marg6mom
% -322.72, -85.7627, -42.8005, -4.23746, -4.26796 nats =
% -1401.56, -372.462, -185.88, -18.403, -18.5355 dB
% correspond to probability ratios of
% 1., 8.11718\times 10^{102}, 3.69524\times 10^{121}, 2.06704\times 10^{138},
% 2.00495\times 10^{138}
%
% difference in relentropies between 4 mom and 2 mom:
% sample level: 279.92 nats = 1215.68 dB
% marg level: 81.5252 nats =  354.059 dB
% difference in relentropies between 6 mom and 4 mom:
% marg level: -0.0305024 nats = -0.13247 dB
% correspond to prob ratios of
% 3.69524\times 10^{121},2.5465\times 10^{35}, 0.969958
%
% comparison_ME_sample_full_levels.nb
%
